Improving credibility and efficiency of decision-making \\ within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex
spell check

We built a full-fletched mobile-friendly web application using Meteor web framework~\cite{meteor}.
Meteor framework supports reactivity which makes the application update user interface based on actions
of other users in real time. This helps users see comments by other users as they happen, but can also see
progress during voting in real time.

@@

Web application contains other features which makes it easier to use as a decision making and discusion
platform, like notifications, and additional features which allow the application to be used also to
help run in-person meetings to discuss discussion items made
online. Facilitators of in-person meetings can use it to prepare agendas for meetings, take notes,
and display summary points of current discussion and what proposals are being voted on. Through that the
application can also serve as way to integrate both online and in-person decision making. Having all of
decision making in one platform serves as an important resource for institutional memory.

PeerMind source code is available under open source licence at \url{https://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{https://redacted.for.blind.review}.
The research protocol with human subjects was approved by \emph{redacted for blind review} under
ID \emph{redacted for blind review}.

@@

In comparison, we analyzed spring 2016 council minutes when community was meeting in-person and
estimated that members spent approximately 2.600.000 seconds total doing decision making
(around 5 hours per member on average).
We estimated this based on information about beginning and end of councils multiplied
with an estimation of the number of people attending each council.
We estimated the number of people attending based on number of votes made for different proposals
and the quorum size, taking the maximum of both.
We find this a good and conservative proxy because councils have a rule that they have to adjurn
if the number of members present fall under the quorum (42 members) for more than 10 minutes
which in practice members discover soon through the number of votes being made or when count
is explictly requested.

@@

In the case of the in-person decision making it is also unclear how much time to spend on each
dicussion item: how contentious the discussion really is can be seen only after voting.
Using PeerMind members can observe the voting process in real-time and continue discussing
and even changing their votes if they get convinced to change their poisition.
At the same time using feedback provided by credibility value they can also gauge how
much discussion is needed.

>>>>

We built a full-fledged mobile-friendly web application using Meteor web framework~\cite{meteor}.
Meteor framework supports reactivity which makes the application update user interface based on actions
of other users in real time. This helps users see comments by other users as they happen, but can also see
progress during voting in real time.

@@

Web application contains other features which makes it easier to use as a decision making and discussion
platform, like notifications, and additional features which allow the application to be used also to
help run in-person meetings to discuss discussion items made
online. Facilitators of in-person meetings can use it to prepare agendas for meetings, take notes,
and display summary points of current discussion and what proposals are being voted on. Through that the
application can also serve as way to integrate both online and in-person decision making. Having all of
decision making in one platform serves as an important resource for institutional memory.

PeerMind source code is available under open source license at \url{https://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{https://redacted.for.blind.review}.
The research protocol with human subjects was approved by \emph{redacted for blind review} under
ID \emph{redacted for blind review}.

@@

In comparison, we analyzed spring 2016 council minutes when community was meeting in-person and
estimated that members spent approximately 2.600.000 seconds total doing decision making
(around 5 hours per member on average).
We estimated this based on information about beginning and end of councils multiplied
with an estimation of the number of people attending each council.
We estimated the number of people attending based on number of votes made for different proposals
and the quorum size, taking the maximum of both.
We find this a good and conservative proxy because councils have a rule that they have to adjourn
if the number of members present fall under the quorum (42 members) for more than 10 minutes
which in practice members discover soon through the number of votes being made or when count
is explicitly requested.

@@

In the case of the in-person decision making it is also unclear how much time to spend on each
discussion item: how contentious the discussion really is can be seen only after voting.
Using PeerMind members can observe the voting process in real-time and continue discussing
and even changing their votes if they get convinced to change their position.
At the same time using feedback provided by credibility value they can also gauge how
much discussion is needed.
